---
title       : Swiss Fertility and Socioeconomic Indicators (1888) Data
subtitle    : The application for analysing data
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

##  Used data
- This application used data with standardized fertility measure and socio-economic indicators for each of 47
French-speaking provinces of Switzerland at about 1888.
```{r,echo = F}
plot(swiss)
```


--- .class #id 

## Variables description

        
- Fertility: common standardized fertility measure
- Agriculture % of males involved in agriculture as occupation
- Examination % draftees receiving highest mark on army examination
- Education % education beyond primary school for draftees.
- Catholic % catholic (as opposed to protestant).
- Infant.Mortality live births who live less than 1 year.


--- .class #id 

## Functionality

This application allows you to analyze how this indicators are related with detection of claster groups: 

1. Please select in app two indicators and see how they are related

2. Please Please select a number of clusters that you want to select the data



--- .class #id 

## Example 
Let's set indicators: Fertility, Education and number of clusters = 5.
```{r echo = F}
 clusters <- kmeans(data.frame(swiss$Fertility, swiss$Education), 5)

 plot(swiss$Fertility, swiss$Education,
                     col = clusters$cluster, xlab="Fertility", ylab="Education",
                     pch = 20, cex = 3)
                points(clusters$centers, pch = 8, cex = 2, lwd = 3)

```



